We have used the MM-GBSA (molecular mechanics combined with generalized Born and surface-area solvation) method to 
estimate the binding free energy for five different ligands binding to the RNA from their equilibrated trajectories. For the RNA-
ligand system:

\begin{equation} \label{eq:MMGBSA_reaction}
R + L \leftrightharpoons R:L
\end{equation}

where, R is the RNA and L is the ligand.
The binding free energy in solution can be estimated to be 

\begin{equation} \label{eq:MMGBSA_delG_equation}
\Delta G_{bind, solv} = \Delta G_{bind, vaccum} + \Delta G_{solv, complex} -(\Delta G_{solv, ligand} + \Delta G_{solv, RNA})
\end{equation}
where $\Delta G_{bind, vaccum} $ is the binding free energy in vaccum, $\Delta G_{solv, complex}$ is the solvation free energy of 
the RNA complex in solution.
$\Delta G_{solv, ligand}$ is the solvation free energy of individual ligand in solution and $\Delta G_{solv, RNA}$ is the solvation free energy of the RNA in solution.
Solvation free energies involves electrostatic and hydrophobic contributions where the hydrophobic contribution is an empirical value while the electrostatic contribution is estimated using the 
Generalized Born equation for each of the above three states.
We can estimate $\Delta G_{bind, vaccum} $ using the following equation:
\begin{equation} \label{}
 \Delta G_{bind, vaccum} = \Delta H_{bind, vaccum} - T \Delta S_{bind, vaccum}
\end{equation}
where $\Delta H_{bind, vaccum}$ is the enthalpy of binding, T is temperature and \Delta S_{bind, vaccum} is the entropy of binding which is estimated using the Normal mode analysis.
This analysis was performed using MMGBSA.py from AmberTools version 21.\cite{MILLER_ROITBERG_2012}

Citation:
@article{MILLER_ROITBERG_2012,
author = {Miller, Bill R. III and McGee, T. Dwight Jr. and Swails, Jason M. and Homeyer, Nadine and Gohlke, Holger and Roitberg, Adrian E.},
title = {MMPBSA.py: An Efficient Program for End-State Free Energy Calculations},
journal = {Journal of Chemical Theory and Computation},
volume = {8},
number = {9},
pages = {3314-3321},
year = {2012},
doi = {10.1021/ct300418h},
    note ={PMID: 26605738},

URL = { 
        https://doi.org/10.1021/ct300418h
    
},
eprint = { 
        https://doi.org/10.1021/ct300418h
    
}

}